---
title: "More Frequency Plots"
author: "Jolie Phan"
date: "version `r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: yes
    toc_depth: 4
    toc_float:
      collapsed: no
  pdf_document:
    toc: yes
    toc_depth: 4
editor_options:
  chunk_output_type: console
---

Plot frequencies of naive and convalescent CD4+ T cells which co-express IFNg and CD154.

Note: all p-values are unadjusted.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.width = 4, fig.height = 5.5)
```

# Load libraries

```{r, message = FALSE}
library(here)
library(flowWorkspace)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(ggbeeswarm)
library(cowplot)
library(ggh4x)
source(here::here("scripts/Helper_Functions.R")) # for make_mag_plots()
```

# Load data

```{r}
save_output <- TRUE

gs <- load_gs(here::here("out/GatingSets/HAARVIVAC_GatingSet_with_COMPASS_Subsets"))

if(!dir.exists(here::here("out/frequency_plots"))) {
    cat(sprintf("Creating folder %s\n", here::here("out/frequency_plots")))
    dir.create(here::here("out/frequency_plots"), recursive = T)
}
```

```{r}
# Arial font setup. Downloaded afms from https://github.com/microsoft/microsoft-r-open/tree/ec3fd89e5fb5794bd8149905c134ad801bb61800
Arial <- Type1Font(family = "Arial",
                   metrics = c(here::here("data/Arial_afm/ArialMT.afm"),
                               here::here("data/Arial_afm/ArialMT-Bold.afm"),
                               here::here("data/Arial_afm/ArialMT-Italic.afm"),
                               here::here("data/Arial_afm/ArialMT-BoldItalic.afm")))
windowsFonts("Arial" = windowsFont("Arial"))
pdfFonts(Arial = Arial)
```

# Add boolean gate

## CD4 IFNg+CD154+

```{r}
# Get paths
cd4_ifng_path <- "/Time/CD3+/CD14-CD19-/Lymphocytes/Singlet/Live/CD4+/IFNg+"
cd4_cd154_path <- "/Time/CD3+/CD14-CD19-/Lymphocytes/Singlet/Live/CD4+/CD154+"

# Add boolean gate
gs_pop_add(gs, eval(substitute(flowWorkspace::booleanFilter(v),
                               list(v = as.symbol(paste0("", cd4_ifng_path,
                                                         "&", cd4_cd154_path))))),
           parent = "/Time/CD3+/CD14-CD19-/Lymphocytes/Singlet/Live/CD4+", name = "IFNg+CD154+")
```

## CD8 CD107a+HLADR+CD38+

```{r, eval=FALSE}
# Get paths
cd8_cd107a_path <- "/Time/CD3+/CD14-CD19-/Lymphocytes/Singlet/Live/CD8+/CD107a+"
hladr_cd38_path <- "/Time/CD3+/CD14-CD19-/Lymphocytes/Singlet/Live/CD8+/CD8_COMPASS_Subsets/HLADR+CD38+"  

# Add boolean gate
gs_pop_add(gs, eval(substitute(flowWorkspace::booleanFilter(v),
                               list(v = as.symbol(paste0("", cd8_cd107a_path,
                                                         "&", hladr_cd38_path))))),
           parent = "/Time/CD3+/CD14-CD19-/Lymphocytes/Singlet/Live/CD8+", name = "CD107a+HLADR+CD38+")
```

Recompute the GatingSet

```{r}
flowWorkspace::recompute(gs)
```

# Extract frequencies

Exclude SEB.

## CD4 IFNg+CD154+

```{r}
cd4_ifng_cd154_parent <- "/Time/CD3+/CD14-CD19-/Lymphocytes/Singlet/Live/CD4+/IFNg+CD154+"

ifng_cd154_counts <- pData(gs) %>%
  tibble::rownames_to_column("rowname") %>%
  left_join(gs_pop_get_count_fast(gs, subpopulations = cd4_ifng_cd154_parent), by = c("rowname" = "name")) %>%
  dplyr::rename(Subpop = Count) %>%
  dplyr::select(rowname, "SAMPLE ID", "EXPERIMENT NAME", "PATIENT ID", Stim, Group, Timepoint, Subpop, ParentCount) %>%
  dplyr::filter(Stim != "SEB") %>%
  mutate(Freq = (Subpop/ParentCount)*100) 

# Add infection status column
i1 <- grepl("H", ifng_cd154_counts$`SAMPLE ID`) 
i2 <- grepl("C", ifng_cd154_counts$`SAMPLE ID`) 
ifng_cd154_counts$Infection_Status <- NULL
ifng_cd154_counts$Infection_Status[i1] <- "Naive"
ifng_cd154_counts$Infection_Status[i2] <- "Conv"
ifng_cd154_counts$Infection_Status <- factor(ifng_cd154_counts$Infection_Status, levels = c("Naive", "Conv"))

ifng_cd154_counts$Group <- factor(ifng_cd154_counts$Group, levels = c("Naive PRE", "Naive POST", "Conv PRE", "Conv POST"))
```

## CD8 CD107a+HLADR+CD38+

```{r, eval=FALSE}
cd8_cd107a_hladr_cd38_parent <- "/Time/CD3+/CD14-CD19-/Lymphocytes/Singlet/Live/CD8+/CD107a+HLADR+CD38+"

cd107a_hladr_cd38_counts <- pData(gs) %>%
  tibble::rownames_to_column("rowname") %>%
  left_join(gs_pop_get_count_fast(gs, subpopulations = cd8_cd107a_hladr_cd38_parent), by = c("rowname" = "name")) %>%
  dplyr::rename(Subpop = Count) %>%
  dplyr::select(rowname, "SAMPLE ID", "EXPERIMENT NAME", "PATIENT ID", Stim, Group, Timepoint, Subpop, ParentCount) %>%
  dplyr::filter(Stim != "SEB") %>%
  mutate(Freq = (Subpop/ParentCount)*100) 

# Add infection status column
i1 <- grepl("H", cd107a_hladr_cd38_counts$`SAMPLE ID`) 
i2 <- grepl("C", cd107a_hladr_cd38_counts$`SAMPLE ID`) 
cd107a_hladr_cd38_counts$Infection_Status <- NULL
cd107a_hladr_cd38_counts$Infection_Status[i1] <- "Naive"
cd107a_hladr_cd38_counts$Infection_Status[i2] <- "Conv"
cd107a_hladr_cd38_counts$Infection_Status <- factor(cd107a_hladr_cd38_counts$Infection_Status, levels = c("Naive", "Conv"))

cd107a_hladr_cd38_counts$Group <- factor(cd107a_hladr_cd38_counts$Group, levels = c("Naive PRE", "Naive POST", "Conv PRE", "Conv POST"))
```

# Plots

```{r}
stims <- c("DMSO", "S1", "S2", "NCAP") 

fill_colors <- list("Naive" = c("Naive PRE" = "#54A8E1", "Naive POST" = "#196293"),
                    "Conv" = c("Conv PRE" = "#EB4D4F", "Conv POST" = "#9D1213"),
                    "PRE" = c("Naive PRE" = "#54A8E1", "Conv PRE" = "#EB4D4F"),
                    "POST" = c("Naive POST" = "#196293", "Conv POST" = "#9D1213"))
```

## CD4 IFNg+CD154+

### Naive PRE vs Naive POST

```{r}
# There is an outlier in the S2-stimmed CD4 IFNg+CD154+ samples, the S2 data will be plotted separately w/o the outlier PTID 
naive_ifng_cd154_plots <- purrr::pmap(.l = list(stims[-3]),
                               .f = function(n) {
                                 make_mag_plots(ifng_cd154_counts, current_stim = n, compare_time = TRUE, keep = "Naive",
                                                groups_to_compare = c("Naive PRE", "Naive POST"), paired = TRUE, fill_colors = fill_colors,
                                                group_by_colname = "Group", subtitle = paste0("IFN", "\U03B3", "+CD154+"), y_axis_text = "% CD4+ T Cells",
                                                ylim = c(0, 1), y_axis_size = 20)
                               })
names(naive_ifng_cd154_plots) <- stims[-3]

ifng_cd154_counts_no_outlier <- ifng_cd154_counts %>%
  dplyr::filter(Stim == "S2") %>%
  dplyr::filter(`PATIENT ID` != "57H")
  
naive_s2_ifng_cd154_plot <- make_mag_plots(ifng_cd154_counts_no_outlier, current_stim = "S2", compare_time = TRUE, keep = "Naive",
                                                groups_to_compare = c("Naive PRE", "Naive POST"), paired = TRUE, fill_colors = fill_colors,
                                                group_by_colname = "Group", subtitle = paste0("IFN", "\U03B3", "+CD154+"), y_axis_text = "% CD4+ T Cells", 
                                           ylim = c(0, 1), y_axis_size = 20)

# naive_ifng_cd154_list <- align_plots(naive_ifng_cd154_plots[["DMSO"]], naive_ifng_cd154_plots[["S1"]], naive_s2_ifng_cd154_plot, naive_ifng_cd154_plots[["NCAP"]], align = "v")
# names(naive_ifng_cd154_list) <- stims
# 
# ggdraw(naive_ifng_cd154_list[["DMSO"]])
# ggdraw(naive_ifng_cd154_list[["S1"]])
# ggdraw(naive_ifng_cd154_list[["S2"]])
# ggdraw(naive_ifng_cd154_list[["NCAP"]])

naive_ifng_cd154_plots[["DMSO"]]
naive_ifng_cd154_plots[["S1"]]
naive_s2_ifng_cd154_plot
naive_ifng_cd154_plots[["NCAP"]]
```

### Conv PRE vs Conv POST

```{r}
conv_ifng_cd154_plots <- purrr::pmap(.l = list(stims),
                               .f = function(n) {
                                 make_mag_plots(ifng_cd154_counts, current_stim = n, compare_time = TRUE, keep = "Conv",
                                                groups_to_compare = c("Conv PRE", "Conv POST"), paired = TRUE, fill_colors = fill_colors,
                                                group_by_colname = "Group", subtitle = paste0("IFN", "\U03B3", "+CD154+"), y_axis_text = "% CD4+ T Cells",
                                                ylim = c(0, 1.75), y_axis_size = 20)
                               })
names(conv_ifng_cd154_plots) <- stims

# conv_ifng_cd154_list <- align_plots(conv_ifng_cd154_plots[["DMSO"]], conv_ifng_cd154_plots[["S1"]], conv_ifng_cd154_plots[["S2"]], conv_ifng_cd154_plots[["NCAP"]], align = "v")
# names(conv_ifng_cd154_list) <- stims
# 
# ggdraw(conv_ifng_cd154_list[["DMSO"]])
# ggdraw(conv_ifng_cd154_list[["S1"]])
# ggdraw(conv_ifng_cd154_list[["S2"]])
# ggdraw(conv_ifng_cd154_list[["NCAP"]])

conv_ifng_cd154_plots[["DMSO"]]
conv_ifng_cd154_plots[["S1"]]
conv_ifng_cd154_plots[["S2"]]
conv_ifng_cd154_plots[["NCAP"]]
```

### Naive PRE vs Conv PRE

```{r}
pre_ifng_cd154_plots <- purrr::pmap(.l = list(stims),
                               .f = function(n) {
                                 make_mag_plots(ifng_cd154_counts, current_stim = n, compare_time = FALSE, keep = "PRE", 
                                                groups_to_compare = c("Naive PRE", "Conv PRE"), paired = FALSE, fill_colors = fill_colors, 
                                                group_by_colname = "Group", subtitle = paste0("IFN", "\U03B3", "+CD154+"), y_axis_text = "% CD4+ T Cells",
                                                y_axis_size = 20)
                               })
names(pre_ifng_cd154_plots) <- stims

# pre_ifng_cd154_list <- align_plots(pre_ifng_cd154_plots[["DMSO"]], pre_ifng_cd154_plots[["S1"]], pre_ifng_cd154_plots[["S2"]], pre_ifng_cd154_plots[["NCAP"]], align = "v")
# names(pre_ifng_cd154_list) <- stims
# 
# ggdraw(pre_ifng_cd154_list[["DMSO"]])
# ggdraw(pre_ifng_cd154_list[["S1"]])
# ggdraw(pre_ifng_cd154_list[["S2"]])
# ggdraw(pre_ifng_cd154_list[["NCAP"]])

pre_ifng_cd154_plots[["DMSO"]]
pre_ifng_cd154_plots[["S1"]]
pre_ifng_cd154_plots[["S2"]]
pre_ifng_cd154_plots[["NCAP"]]
```

### Naive POST vs Conv POST

```{r}
post_ifng_cd154_plots <- purrr::pmap(.l = list(stims),
                               .f = function(n) {
                                 make_mag_plots(ifng_cd154_counts, current_stim = n, compare_time = FALSE, keep = "POST", 
                                                groups_to_compare = c("Naive POST", "Conv POST"), paired = FALSE, fill_colors = fill_colors, 
                                                group_by_colname = "Group", subtitle = paste0("IFN", "\U03B3", "+CD154+"), y_axis_text = "% CD4+ T Cells",
                                                ylim = c(0, 2.75), y_axis_size = 20)
                               })
names(post_ifng_cd154_plots) <- stims

# post_ifng_cd154_list <- align_plots(post_ifng_cd154_plots[["DMSO"]], post_ifng_cd154_plots[["S1"]], post_ifng_cd154_plots[["S2"]], post_ifng_cd154_plots[["NCAP"]], align = "v")
# names(post_ifng_cd154_list) <- stims
# 
# ggdraw(post_ifng_cd154_list[["DMSO"]])
# ggdraw(post_ifng_cd154_list[["S1"]])
# ggdraw(post_ifng_cd154_list[["S2"]])
# ggdraw(post_ifng_cd154_list[["NCAP"]])

post_ifng_cd154_plots[["DMSO"]]
post_ifng_cd154_plots[["S1"]]
post_ifng_cd154_plots[["S2"]]
post_ifng_cd154_plots[["NCAP"]]
```



# Save figures

```{r save boxplots pdf}
if(save_output) {
  cairo_pdf(file=here::here("out/frequency_plots/CD4_naive_ifng_cd154_plot.pdf"), width=4, height=5.5,
        onefile = TRUE, bg = "transparent", family = "Arial") # default unit is inches, default font is Helvetica.
  # print(ggdraw(naive_ifng_cd154_list[["DMSO"]]))
  # print(ggdraw(naive_ifng_cd154_list[["S1"]]))
  # print(ggdraw(naive_ifng_cd154_list[["S2"]]))
  # print(ggdraw(naive_ifng_cd154_list[["NCAP"]]))
  print(naive_ifng_cd154_plots[["DMSO"]])
  print(naive_ifng_cd154_plots[["S1"]])
  print(naive_s2_ifng_cd154_plot)
  print(naive_ifng_cd154_plots[["NCAP"]])
  dev.off()
  
    cairo_pdf(file=here::here("out/frequency_plots/CD4_conv_ifng_cd154_plot.pdf"), width=4, height=5.5,
        onefile = TRUE, bg = "transparent", family = "Arial") # default unit is inches, default font is Helvetica.
  # print(ggdraw(conv_ifng_cd154_list[["DMSO"]]))
  # print(ggdraw(conv_ifng_cd154_list[["S1"]]))
  # print(ggdraw(conv_ifng_cd154_list[["S2"]]))
  # print(ggdraw(conv_ifng_cd154_list[["NCAP"]]))
  print(conv_ifng_cd154_plots[["DMSO"]])
  print(conv_ifng_cd154_plots[["S1"]])
  print(conv_ifng_cd154_plots[["S2"]])
  print(conv_ifng_cd154_plots[["NCAP"]])
  dev.off()
  
      cairo_pdf(file=here::here("out/frequency_plots/CD4_post_ifng_cd154_plot.pdf"), width=4, height=5.5,
        onefile = TRUE, bg = "transparent", family = "Arial") # default unit is inches, default font is Helvetica.
  # print(ggdraw(post_ifng_cd154_list[["DMSO"]]))
  # print(ggdraw(post_ifng_cd154_list[["S1"]]))
  # print(ggdraw(post_ifng_cd154_list[["S2"]]))
  # print(ggdraw(post_ifng_cd154_list[["NCAP"]]))
  print(post_ifng_cd154_plots[["DMSO"]])
  print(post_ifng_cd154_plots[["S1"]])
  print(post_ifng_cd154_plots[["S2"]])
  print(post_ifng_cd154_plots[["NCAP"]])
  dev.off()
}
```